---
title: "CoVenture Anxiety Outcomes 20 March 2024"
author: "Samantha J. Lynch"
output:  
  html_notebook:
    theme: paper
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    fig.width = 7,
    tidy = TRUE
)

## turn off scientific notation 
options(scipen=999)
```

```{r libraries, options}
# Load libraries
library(tidyverse) #
library(haven)  # load and work with SPSS data files
library(summarytools) # for summary statistics
library(gtsummary) # for summary statistics
library(ggthemes)
library(lme4) #frequentist regression models
library(brms) # Bayesian Regression Models
library(StanHeaders) # need to laod this for brms
library(data.table) # wrangling and formatting data and tables
library(formattable)
library(broom)
library(finalfit)
library(knitr)
library(emmeans)
library(ggeffects)
library(tidybayes)

## set theme
theme_gtsummary_journal(journal = "jama")
theme_gtsummary_compact()

```

# Anxiety 

## Gaussian 
```{r depression gaussian, options, echo=TRUE, results='asis'}
mod_anx_cont <- brm(ANX ~ 1 + DEM_01 + Exp_Group + Language + year + year:Exp_Group + (1|id+schoolnum),  
               data = cov_5, 
               family = gaussian,
               warmup = 1000, iter = 4000, 
               cores = 4, chains = 4, 
               seed = 123,
               control = list(adapt_delta = 0.9)) #increasing for better convergence     
```


### Results {.tabset}

#### Summary
```{r depression gaussian results summary, echo=FALSE}
summ_mod_anx_cont=summary(mod_anx_cont)
formattable(summ_mod_anx_cont$fixed)


```

#### Detailed
```{r depression gaussian results detailed, echo=FALSE}
summ_mod_anx_cont
```

### Model quality checks
#### Plot predicted data using posterior predictive checks
```{r Plot density of data vs model predicted data}
pp_check(mod_anx_cont)
```
#### Plot variables and traceplots

```{r traceplots}
plot(mod_anx_cont,
     variable = "^b_", regex = TRUE, # only plot population level
     plot = TRUE, ask = FALSE, newpage=FALSE) 
```
#### Plot predicted response for the different predicotrs
```{r conditional effects anx}
plot(conditional_effects(mod_anx_cont), plot = TRUE, ask = FALSE, newpage=FALSE)
```

## Gamma 
```{r depression gamma, echo=TRUE, results='hide'}
mod_anx_gamma <- brm(ANX ~ 1 + DEM_01 + Exp_Group + Language + year + year:Exp_Group + (1|id+schoolnum),  
               data = cov_5, 
               family = hurdle_gamma(link = "log"),
               warmup = 1000, iter = 4000, 
               cores = 4, chains = 4, 
               seed = 123,
               control = list(adapt_delta = 0.9)) #increasing for better convergence     
```
### Results {.tabset}
#### Summary
```{r depression gamma results summary}
summ_mod_anx_gamma=summary(mod_anx_gamma)
formattable(summ_mod_anx_gamma$fixed)
```
#### Detailed
```{r depression gamma results}
summ_mod_anx_gamma
```
### Model quality checks
#### Pairs plot (as suggested by BRMS)
I'm not really sure how to interpret this. 
```{r pairs plot, fig.height=10}
pairs(mod_dep_gamma)
```

#### Plot predicted data using posterior predictive checks
```{r Gamma Plot density of data vs model predicted data}
pp_check(mod_anx_gamma)
```

#### Plot variables and traceplots
```{r gamma traceplots}
plot(mod_anx_gamma,
     variable = "^b_", regex = TRUE, # only plot population level
     plot = TRUE, ask = FALSE, newpage=FALSE) 
```

#### Plot predicted response for the different predicotrs
```{r gamma conditional effects anx,fig.height=5}
plot(conditional_effects(mod_anx_gamma),plot = TRUE, ask = FALSE, newpage=FALSE)
```

## Plots of raw data

```{r distribution anx, fig.height=5}
# Assuming 'cov_5' is your data frame and 'ANX' is the response variable
hist(cov_5$ANX, main = "Histogram of ANX", xlab = "ANX")

# Add a line at y = 0 for reference
abline(h = 0, col = "red")

# Add a vertical line at x = 0 for reference
abline(v = 0, col = "blue")
```

```{r boxplot anx, fig.height=5}
boxplot(cov_5$ANX, main = "Boxplot of ANX")
```

